% Packages go here
\usepackage[acronym]{glossaries}
\usepackage{nomencl}
\usepackage{indentfirst}
\usepackage{bbm}
\usepackage{float}
\usepackage{graphicx}
\usepackage{longtable}

\makenomenclature
\makeglossaries

% Document Details
\title{Soccer Match Prediction}
\author{Group 3 - Bardia Parmoun \& Christopher Semaan}
\date{April 2025}

\degree{SYSC 5108: Deep Learning}
\program{MASc Electrical and Computer Engineering}
\college{Carleton University}

\location{Ottawa, Ontario}
\submissiondate{April 2025}

% PDF meta-info:
\subjectline{\@title}
\keywords{keyword 1, keyword 2, etc.}

\abstract{%
    Soccer is among the most popular sports around the world, and soccer matches attract millions of fans annually. This popularity has led to the growth sports betting market. Sports betting, especially on a complex game like soccer, comes with its own set of challenges due to the numerous known and unknown factors. As a result, it is a very good use case for the application of various machine learning techniques. This paper explores the use of deep learning, more specifically a multi-layered Feedforward Neural Network (\gls{fnn}), to predict the outcome of soccer matches. The model is able to predict home wins, away wins, and draws using a variety of historical and predictive features. The performance of the model was also compared with the pre-match odds of each game and it was concluded that the model performs almost as accurately as the professional odds-makers. With an accuracy that outperforms random choice by $15\%$, this paper showcases promising results for the use of machine learning in the realm of sports betting.
}

\acknowledgements{%
    The authors of this paper would like to express their sincere gratitude to Dr. Changcheng Huang for his great efforts, guidance, expert knowledge, and warm support throughout the semester. 
}

\newcommand{\mainmatter}{
    \pagenumbering{arabic}
    \setcounter{page}{1}
}